Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-28 cbm-rbd-paper.tex
one figure for sim prosp. costrate

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim1fig5}
\includegraphics[width=0.5\textwidth]{br1sim2fig5}
\includegraphics[width=0.5\textwidth]{br1sim3fig5}
\includegraphics[width=0.5\textwidth]{br1sim4fig5}
\caption{***Simulation study with ***prsopective costrate criterion***, $\tthresh = 0.5$.
TL: $\lambda_k =     \ykz$,
TR: $\lambda_k = 0.5 \ykz$,
BL: $\lambda_k = 2   \ykz$,
BR: $\lambda_k = 0.2 \ykz$}
\label{fig:simprospcostrate05}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
\caption{***Simulation study with ***total costrate criterion***, $\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
\label{fig:simtotalcostrate0102}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim1fig5}
\includegraphics[width=0.5\textwidth]{br1sim2fig5}
\includegraphics[width=0.5\textwidth]{br1sim3fig5}
\includegraphics[width=0.5\textwidth]{br1sim4fig5}
\caption{***Simulation study with ***prospective costrate criterion***, $\tthresh = 0.5$.
TL: $\lambda_k =     \ykz$,
TR: $\lambda_k = 0.5 \ykz$,
BL: $\lambda_k = 2   \ykz$,
BR: $\lambda_k = 0.2 \ykz$}
\label{fig:simprospcostrate05}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
\caption{***Simulation study with ***total costrate criterion***, early failures ($0.5 \times$ MTTF),
$\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
\label{fig:simtotalcostrate0102}
\end{figure}
